The K2 Bright Star Survey

### 2019-05-06 paper/ms.tex
something in the abstract
formatting

\author[0000-0003-2595-9114]{Benjamin J. S. Pope}
\affiliation{Center for Cosmology and Particle Physics, Department of Physics, New York University, 726 Broadway, New York, NY 10003, USA}
\affiliation{NASA Sagan Fellow}

@@

%% Mark off the abstract in the ``abstract'' environment. 
\begin{abstract}
While the \kepler\ mission was designed to look at tens of thousands of faint stars ($V \gtrsim 12$), brighter stars which saturate the detector are nevertheless some of the most interesting because of the ease with which they can be observed by other instruments and the wealth of knowledge about them that is already available. By considering the unsaturated scattered light `halo' around these stars we retrieve precise light curves of most of the brightest stars in \ktwo fields from Campaign~4 onwards. This bright star survey reveals stellar variability ubiquitously, including effects of stellar pulsation, rotation, and binarity. Here we describe our pipeline, and present a catalogue of the bright stars studied, with classifications and parametrizations of their variability and remarks on interesting objects. These light curves are publicly available as a High Level Science Product from the Mikulski Archive for Space Telescopes (MAST). \href{https://github.com/benjaminpope/k2halo}{\color{linkcolor}\faGithub} % git link shamelessly borrowed from Luger!
\end{abstract}

@@

\begin{align}
\forall_j w_j &> 0\\
\sum_i f_i  &= N
\end{align}

@@

The objective function $\Lambda_{k,l}$ is the $L_k$ norm on a `lagged' finite difference with a lag parameter $l$. For $k = 1$ and $l = 1$, $\Lambda_{1,1}$ is the standard Total Variation objective (TV) used in previous halo papers, and can be seen as the L1 norm on the derivative of $f$ or as a discrete approximation to its arc length. The $L=2$ L2 Variation (L2V) is sometimes referred to in image processing literature as the `smoothness' regularizer, as it seeks to penalize large gradients without necessarily making them sparse. The lag parameter $l$ allows for flexibility in modelling systematics occurring at different timescales from cadence-to-cadence, and we investigate its effects below. The order parameter $k$ allows for flexibility in how sensitive we are to normally-distributed versus long-tailed noise.

>>>>

\author[0000-0003-2595-9114]{Benjamin J. S. Pope}
\affiliation{Center for Cosmology and Particle Physics, Department of Physics, New York University, 726 Broadway, New York, NY 10003, USA}
\affiliation{Center for Data Science, New York University, 60 Fifth Ave, New York, NY 10011, USA}
\affiliation{NASA Sagan Fellow}

@@

%% Mark off the abstract in the ``abstract'' environment. 
\begin{abstract}
While the \kepler\ mission was designed to look at tens of thousands of faint stars ($V \gtrsim 12$), brighter stars which saturate the detector are nevertheless some of the most interesting because of the ease with which they can be observed by other instruments and the wealth of knowledge about them that is already available. By considering the unsaturated scattered light `halo' around these stars we retrieve precise light curves of most of the brightest stars in \ktwo fields from Campaign~4 onwards. The halo method is highly agnostic about the cause and form of systematics and we show that it nevertheless it is effective at extracting light curves from both normal and saturated stars. This bright star survey reveals stellar variability ubiquitously, including effects of stellar pulsation, rotation, and binarity. Here we describe our pipeline, and present a catalogue of the bright stars studied, with classifications and parametrizations of their variability and remarks on interesting objects. These light curves are publicly available as a High Level Science Product from the Mikulski Archive for Space Telescopes (MAST). \href{https://github.com/benjaminpope/k2halo}{\color{linkcolor}\faGithub} % git link shamelessly borrowed from Luger!
\end{abstract}

@@

\begin{align}
\forall_j w_j &> 0\\
\sum_{i=1}^{N} f_i  &= N
\end{align}

@@

The objective function $\Lambda_{k,l}$ is the $L_k$ norm on a `lagged' finite difference with a lag parameter $l$. For $k = 1$ and $l = 1$, $\Lambda_{1,1}$ is the standard Total Variation objective (TV) used in previous halo papers, and can be seen as the L1 norm on the derivative of $f$ or as a discrete approximation to its arc length. The L2 Variation (L2V) with $k=2$ is sometimes referred to in image processing literature as the `smoothness' regularizer, as it seeks to penalize large gradients without necessarily making them sparse. The lag parameter $l$ allows for flexibility in modelling systematics occurring at different timescales from cadence-to-cadence, and we investigate its effects below. The order parameter $k$ allows for flexibility in how sensitive we are to normally-distributed versus long-tailed noise.
